\documentclass[a4paper,13pt]{article}
\begin{document}
\pagenumbering{arabic}
\title{ HOW TO DO RUNNING EVERY DAY.}
\author{Mutonerwa Stephen Musaazi    Reg:  15/U/744   StudentNo:  215000283}
\maketitle
\section{Abstract}
The objective of this report is t the steps people take usually before starting running, the benefits of running on your life, how to void and prevent injuries, and times people do usually run in the different weather periods.
\section{Introduction }
{
Running is a daily routine most of the people do every day especially in the morning and evening hours. People, during rainy days it is an easy time to stay inside in bed mostly during morning hours. But during rainy days more and more people are turning toward running in the evening to stay motivated. Running at least one Kilometer every single day, throughout the year is very essential to your life, and more important if you are the kinds of people who sit from morning to evening.
Ever since I started running there has been an increasing number of people from different life classes running, but these numbers mostly depend on the weather that is rainy and sunny months of the year.
Hot months like January. Many people usually run in the morning hours starting from 5:45hours to 6:30hour them after they get prepared for work or schooling for my fellow university students I run with. This means that more people run in the evening during these wet months.
For the purposes of this report is to teach people, how they should run such that they benefit from it.}
\section{Methodology}
{This research was conducted based on the information I know and also asking my fellow runners. Runners gave me some lectures on things they do every day they go for running.}
\section{How to prepare for running at your very start time.}
\subsection{Make Sure You’re Ready}{
If you decide to run every day, you should be running at moderately low speed, and willing to run short distances. Think at small first. Don’t think, to going to run every day for a year. Start with a month. If you were running five days a week before, run just one a kilometer on days six and seven. Increasing mileage too quickly can raise your chance of injury. The best thing to do before beginning is slowly build up your mileage base. Then when you are ready to begin running every day, it won’t be such a shock to your system. You can run the same number of weekly miles spread over seven days instead of five to help your body adjust.}
\subsection{Prevent Injury}{
Prevention of injury is an after-thought for most runners, which is a big mistake, It should be built into the training itself, specifically strength exercises, getting enough sleep, and using a foam roller for any tight or sore muscles.}
\subsection{After running}{
To cool down properly, jog slowly for 5 to 10 minutes. After that, perform bodyweight exercises to target other muscles groups. A 15-minute routine of jumping jacks will help strengthen your muscles and reduce post-workout tightness.
Maintaining your fluid intake throughout the day is critical. After running, you'll need to replace fluids you lost through sweating. A few glasses of water can make a big difference. If your urine is the color of lemonade or lighter, you're properly hydrated. If it's darker, you need more water.
You'll also need to replace electrolytes, which can be found in sports drinks, smart water products, gels, chews or salt tablets. If you prefer real food instead of processed sports nutrition, you can also find electrolytes (such as sodium, potassium, magnesium and calcium) in foods like bananas, avocados.
 Static stretching is an excellent way to reduce post-workout muscle soreness and maintain good flexibility. Static stretches are held for 30 seconds, as opposed to dynamic stretches that involve continuous movement. To avoid injury, static stretches should never be forced. Move slowly into the stretch until you feel the first bit of tension in the muscle, and hold there.  }
\section{conclusion}{
I have benefit much in running and I think everybody should start doing it because it is healthy, big people in size running helps you to cut that weight, because during running, people sweat a lot and fats also melt.}
\end{document}